Gradual Soundness: Lessons from Static Python

### 2022-01-31 pj-7.1/paper.tex
pj: author order
pj: add deltablue commit
pj: hiding for submission
- remove nbody
- hide acks
- add threats to the microbenchmark section

\author[a]{Kuang-Chen Lu}
\authorinfo{(\email{LuKuangchen1024@gmail.com}) } %% { is a PhD student at Brown University.}
\affiliation[a]{Brown University, Providence, RI, USA}
\author[a]{Ben Greenman}
\authorinfo{(\email{benjamin.l.greenman@gmail.com}) } %% {is a PLT member and a postdoc at Brown University.}
\author[b]{Carl Meyer}
\authorinfo{(\email{carljm@fb.com}) } %% FILL
\affiliation[b]{Meta, Menlo Park, CA, USA}
\author[b]{Dino Viehland}
\authorinfo{(\email{dinoviehland@fb.com}) } %% FILL
\author[a]{Shriram Krishnamurthi}
\authorinfo{(\email{shriram@brown.edu}) } %% {is the Vice President of Programming Languages (no, not really) at Brown University.}

@@

\begin{table}[t]
  \caption{Microbenchmark performance ratios. NB: data for nbody is pending.}
  %% FILL don't forget to update \numbenchmark{}
  \label{t:microbenchmark}

  \centering
  \begin{tabular}{lrr}
    Name               & Typed / Python & Refined / Python \\\midrule
    \bmname{deltablue} &         0.59 &           0.30 \\
    \bmname{nbody}     &         FILL &           FILL \\
    \bmname{richards}  &         0.53 &           0.22 \\
    \bmname{fannkuch}  &         1.03 &           0.46
    %% fannkuch typedbasic2 = 0.90
  \end{tabular}
\end{table}

@@

%% FILL threats to validity

@@

\acks{
  \SP{} was developed by Sinan Cepel, William Meehan, Carl Meyer, Aniket Panse,
  and Dino Viehland.
  The Brown authors contributed to the language by modeling it independently; they
  are not part of the \SP{} team.

  Special thanks to Guido van Rossum for helping the authors meet via Twitter
  and for his ongoing contributions to Python.
  This work was partly supported by the US National Science Foundation.
  Greenman acknowledges support from NSF grant 2030859 to the CRA for the \href{https://cifellows2020.org}{CIFellows} project.
}

@@

Benchmarks run on the following commit:

@@

>>>>

\author[a]{Kuang-Chen Lu}
\authorinfo{(\email{LuKuangchen1024@gmail.com}) } %% { is a PhD student at Brown University.}
\affiliation[a]{Brown University, Providence, RI, USA}
\author[a]{Ben Greenman}
\authorinfo{(\email{benjamin.l.greenman@gmail.com}) } %% {is a PLT member and a postdoc at Brown University.}
\author[b]{Carl Meyer}
\authorinfo{(\email{carljm@fb.com}) } %% FILL
\affiliation[b]{Meta, Menlo Park, CA, USA}
\author[b]{Dino Viehland}
\authorinfo{(\email{dinoviehland@fb.com}) } %% FILL
\author[b]{Aniket Panse}
\authorinfo{(\email{aniketpanse@fb.com}) } %% FILL
\author[a]{Shriram Krishnamurthi}
\authorinfo{(\email{shriram@brown.edu}) } %% {is the Vice President of Programming Languages (no, not really) at Brown University.}

@@

\begin{table}[t]
  \caption{Microbenchmark performance ratios}
  %% FILL don't forget to update \numbenchmark{}
  \label{t:microbenchmark}

  \centering
  \begin{tabular}{lrr}
    Name               & Typed / Python & Refined / Python \\\midrule
    \bmname{deltablue} &         0.59 &           0.30 \\
    %% \bmname{nbody}     &         FILL &           FILL \\
    \bmname{richards}  &         0.53 &           0.22 \\
    \bmname{fannkuch}  &         1.03 &           0.46
    %% fannkuch typedbasic2 = 0.90
  \end{tabular}

@@

%% \textbf{Note to Programming Reviewers:}
%%  We plan to add a fourth benchmark to \cref{t:microbenchmark}.

\paragraph{Threats to Validity}

\Cref{t:microbenchmark} does not analyze benchmark configurations that mix
typed and untyped code. %% ---only fully-typed and untyped configurations.
Mixed configurations may reveal performance bugs similar to those found
by an evaluation of Retifulated Python~\cite{gm-pepm-2018}.

%% Although mixed configurations are unlikely to have disastrous
%% overhead~\cite{tfgnvf-popl-2016} due to \SP's efficient strategy for enforcing
%% types and Instagram's positive experience with mixed-typed code in
%% production~(\cref{s:migration-path}), they could reveal performance bugs
%% similar to those found by a prior evaluation of Retifulated
%% Python~\cite{gm-pepm-2018}.

@@

%\acks{
%  \SP{} and the Cinder JIT were developed by
%  Max Bernstein,
%  John Biesnecker,
%  Jacob Bower,
%  Sinan Cepel,
%  Tiansi Hu,
%  Orvid King,
%  Vladimir Matveev,
%  William Meehan,
%  Carl Meyer,
%  Matt Page,
%  Aniket Panse,
%  Brett Simmers,
%  Andrei Talaba,
%  Dino Viehland,
%  and Shiyu Wang.
%  The Brown authors contributed to the language by modeling it independently; they
%  are not part of the \SP{} team.
%
%  Special thanks to Twitter, thanks to which the two teams
%  (specifically, Meyer and Krishnamurthi) met.
%  This work was partly supported by the US National Science Foundation.
%  Greenman acknowledges support from NSF grant 2030859 to the CRA for the \href{https://cifellows2020.org}{CIFellows} project.
%}

@@

Benchmarks \bmname{richards} and \bmname{fannkuch} ran on the following commit:

@@

\noindent\bmname{deltablue} ran on a later commit:

\begin{center}
\footnotesize\url{https://github.com/facebookincubator/cinder/commit/c9d14c4474facfeca15b618015b58b99a3e86d25}
\end{center}
